\LARGE \bf Multi-dimensional Optimization of Gasoline-fueled Variable Pitch Multirotor Aircraft

### 2016-04-13 paper.tex

When simultaneously optimizing with 3, 5, and 7 kg payloads our optimizer converges to an optimal solution. The solution flight time is at least 42.46 minutes with a payload less then 7 kg. The values of the optimal design variables can be seen in table~\ref{table:unbound_results}.

>>>>

When simultaneously optimizing with 3, 5, and 7~kg payloads our optimizer converges to an optimal solution. The solution flight time is at least 42.46~minutes with a payload not greater than 7~kg. The values of the optimal design variables can be seen in table~\ref{table:unbound_results}.
